---
title: "OHWM-hex"
format: html
---



## Example from FMG
Mike D was unable to recover the original code used to create the current FG hex graphics. The FG hexs must be recreated and documented here. The code below was copied from [FMG-hex](https://github.com/ForestManagementGeodatabase/FMG-hex)

```{r}
library(hexSticker)
library(magick)
```

```{r}
library(showtext)
## Loading Google fonts (http://www.google.com/fonts)
sysfonts::font_add_google(name = "Ubuntu Condensed", family = "Ubuntu Condensed")
## Automatically use showtext to render text for future devices
showtext_auto()

```{r}
fg_ohwm_hex_image <- "images/ohwm_hex_image.png"

filename <- "FG_hexes/fg-ohwm-hex_1.png"

fg <- sticker(subplot = fg_ohwm_hex_image, 
               s_x = 1,
               s_y = 1,
               s_width = 1.4,
               package = "Ordinary Highwater Mark\nRAT",
               p_x = 1,
               p_y = .48,
               lineheight = 0.3,
               p_color = "bisque",
               p_family = "Ubuntu Condensed",
               p_size = 12,
               h_size = 3,
               h_color = "darkorange4",
               white_around_sticker = TRUE,
               filename = filename)

fuzz <- 50
p <- image_read(filename)
pp <- p %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = "+1+1") %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+", image_info(p)$width-1, "+1")) %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+1", "+", image_info(p)$height-1)) %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+", image_info(p)$width-1, "+", image_info(p)$height-1))
image_write(image = pp, path = "FG_hexes/fg_ohwm_hex_image.png")
file.show("fg_ohwm_hex_image.png")
```