---
title: "fg_tb_hex"
format: html
---

```{r}
library(hexSticker)
library(magick)
```

```{r}
library(showtext)
## Loading Google fonts (http://www.google.com/fonts)
sysfonts::font_add_google(name = "Nanum Pen Script", family = "Nanum Pen Script")
## Automatically use showtext to render text for future devices
showtext_auto()

```{r}
fg_fgtb_hex<- "images/pexels-baskincreativeco-1480807.png"

filename <- "FG_hexes/fg_fgtb-hex.png"

fg <- sticker(subplot = fg_fgtb_hex, 
               s_x = 1,
               s_y = 1,
               s_width = 1.4,
               package = "FluvialGeomorph\nArcGIS Toolbox",
               p_x = 1,
               p_y = 1,
               lineheight = .3,
               p_color = "#4F9E99",
               p_family = "Nanum Pen Script",
               p_size = 12,
               h_size = 3,
               h_color = "#AA555A",
               white_around_sticker = TRUE,
               filename = filename)

fuzz <- 50
p <- image_read(filename)
pp <- p %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = "+1+1") %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+", image_info(p)$width-1, "+1")) %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+1", "+", image_info(p)$height-1)) %>%
  image_fill(color = "transparent", refcolor = "white", fuzz = fuzz, point = paste0("+", image_info(p)$width-1, "+", image_info(p)$height-1))
image_write(image = pp, path = "FG_hexes/fg_fgtb-hex.png")
file.show("fg_fgtb-hex.png")
```